SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-09-10 scipy-1.0/paper.tex

Fortran, despite its age, is still a high-performance scientific programming language with
continued contemporary usage\cite{Koelbel:1993:HPF:562354}. Thus, we wrap the following excellent, field-tested Fortran
libraries in order to provide Python convenience while benefiting from their performance:
FFTPACK\cite{SWARZTRAUBER198445, SWARZTRAUBER198251}, % for performing Fourier transforms,
ODEPACK\cite{hindmarsh1983odepack}, % for solving ordinary differential equation initial value problems,
QUADPACK\cite{piessens1983quadpack}, % for numerical integration of one-dimensional functions,
FITPACK\cite{Dierckx:1993:CSF:151103}, % for curve-fitting and interpolation,
ODRPACK\cite{ODRPACK_Boggs}, % for orthogonal distance regression,
MINPACK\cite{osti_6997568}, % for minimization of linear and nonlinear equations,
ARPACK\cite{leh:sor:yan96}, % for solving large scale eigenvalue problems,
ALGORITHM 644\cite{Amos:1986:APP:7921.214331}, and % for Bessel Functions, and
CDFLIB\cite{CDFLIB_site}. % for evaluation of cumulative density functions.

Rounding out the top three languages in SciPy is C, which is also extremely
well-established over several decades\cite{Kernighan:1988:CPL:576122} of
scientific computing. The C libraries that we wrap in SciPy include
trlib\cite{doi:10.1080/10556788.2018.1449842}, % (iterative solving of the trust region problem),
SuperLU\cite{li05,superlu_ug99}, % (solution of large, sparse, nonsymmetric systems of linear equations),
Qhull\cite{Barber:1996:QAC:235815.235821}, and % (computational geometry)
Cephes\cite{cephes_netlib}. % (mathematics algorithms).

>>>>

Fortran, despite its age, is still a high-performance scientific programming language with
continued contemporary usage\cite{Koelbel:1993:HPF:562354}. Thus, we wrap the following excellent, field-tested Fortran
libraries in order to provide Python convenience while benefiting from their performance:
QUADPACK\cite{piessens1983quadpack} and ODEPACK\cite{hindmarsh1983odepack} for numerical integration
and solution of initial value problems;
FITPACK\cite{Dierckx:1993:CSF:151103}, ODRPACK\cite{ODRPACK_Boggs}, and MINPACK\cite{osti_6997568} for
curve-fitting and least-squares minimization;
FFTPACK\cite{SWARZTRAUBER198445, SWARZTRAUBER198251} for performing Fourier transforms;
ARPACK\cite{leh:sor:yan96} for solving eigenvalue problems;
ALGORITHM 644\cite{Amos:1986:APP:7921.214331} for computing Bessel Functions; and
CDFLIB\cite{CDFLIB_site} for evaluating cumulative density functions.

Rounding out the top three languages in SciPy is C, which is also extremely
well-established over several decades\cite{Kernighan:1988:CPL:576122} of
scientific computing. The C libraries that we wrap in SciPy include
trlib\cite{doi:10.1080/10556788.2018.1449842} for optimization, % (iterative solving of the trust region problem),
SuperLU\cite{li05,superlu_ug99} for solving sparse linear systems, % (solution of large, sparse, nonsymmetric systems of linear equations),
Qhull\cite{Barber:1996:QAC:235815.235821} for computational geometry, and % (computational geometry)
Cephes\cite{cephes_netlib} for special functions. % (mathematics algorithms).
